\documentclass[11pt]{article}
\title{\textbf{{\color{blue}Flex Friday Exploratory Project Proposal}}}
\author{And/Ore Backend Team}
\date{}
\usepackage{tikz}
\usepackage{gensymb}
\usepackage{physics}
\usepackage{color}
\usepackage{tabto}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\begin{document}

\maketitle

\section{{\color{blue}Vision}}

\subsection{{\color{blue}Purpose}}

The team's vision for AndOre is a browser centric top down two dimensional MMO. Built to explore machine learning, AndOre requires a robust and dependable server architecture allowing synergistic application of And/Ore’s team at large. Bringing the team's efforts to fruition requires internal efficient implementation and asynchronous communication between the project and the world at large.
 
The team is responsible for developing the tools to analyze aggregated data so frontend can further evolve the user experience. The backend ultimately provides a brick-and-mortar foundation to further the game's development.

\subsection{{\color{blue}Goal}}

\begin{itemize}
\item Implement a communication tool to improve user experience
\item Optimise server performance
\item Improve gameplay through new game mechanics
\end{itemize}

\section{{\color{blue}Approach}}


\subsection{{\color{blue}Objectives}}

\begin{itemize}
	\item Optimize Server Performance
		\begin{itemize}
			\item Research server architecture
			\item Gain understanding of server tick rate
			\item Change server tick rate
		\end{itemize}
	\item Implement a communication tool to improve the experience of the user
		\begin{itemize}
			\item Research python communication protocols
			\item Add social features such as chat within corporations and general chat
			\item Implement a form of identifying players, such as usernames.
		\end{itemize}
	\item Improve gameplay through new game mechanics
		\begin{itemize}
			\item Implement sprint feature
			\item Implement stamina feature
			\item Implement further suggestions from the rest of the And/Ore team
		\end{itemize}
\end{itemize}

\subsection{{\color{blue}Team}}

{\large {\color{orange}John Z}}

John has experience in working on all parts of a software project, and has a million different projects he could be working on, but chose to be a founder of And/Ore due to his interests in Machine Learning, as he eventually wants to experiment in combining it with IoT, specially due to the connotations. John also has a tendency to write runoff sentences, and thinks Illeism is silly, but that's just what you do in bios.


{\large {\color{orange}Finnigan McDonough}}

Finn is a ninth grade student who has experience in web fundamentals. He hopes to gain experience with server architecture, and coding in general.

{\large {\color{orange}Noah Flewelling}}

Noah is a ninth grader who has experience in horseback riding and 3D printing. He hopes to learn more about coding and server nodes.

{\large {\color{orange} Antonio Custodio}}

\sout{
Antonio is a ninth grader high school student . He has been programming C++  C\# for 2 years. He hasper  He plays hockey  and skateboards for a living.  He plays piano, guitar, flute, dizi, ocarina and violin. He has coded many Xbox 360 stealth servers for a year.
}

Antonio is a ninth grader who's been programming in the C family for more than 2 years. He plays hockey and skateboards for a living. He plays many instruments, including but not limited to: the piano, the guitar, the flute, the dizi, the ocarina, and the violin. He’s set up many xbox 360 stealth servers for years.


{\large {\color{orange} Xander Lemieux}}

Xander is a ninth grader who has experience in C\# due to developing 5 games in unity. He has experience modeling in Maya and Blender, making him a useful resource if there was ever a 3d spinoff of andore. He plays the saxophone, guitar, and launchpad. He also has experience in 3D printing, vive game development, and filmmaking. 

\subsection{{\color{blue}Milestones}}

\begin{itemize}
	\item 10/01/16
		\begin{itemize}
			\item Version 1.4 Release
				\begin{itemize}
					\item Introduced feeding treats to your neural network.
					\item Split up game server for better performance and to introduce the start of multiple playable worlds.
				\end{itemize}
		\end{itemize}
	\item 10/15/16
		\begin{itemize}
			\item Version 1.5 Release
				\begin{itemize}
					\item Bug Fixes
					\item The release of sphere, an admin panel for game moderators
					\item New feature to heal others/buildings.
				\end{itemize}
		\end{itemize}
	\item 10/29/16
		\begin{itemize}
			\item Version 1.6 Release
				\begin{itemize}
					\item Chat Introduced
					\item Bug Fixes
				\end{itemize}
		\end{itemize}
	\item 11/11/16
		\begin{itemize}
			\item Prototype of Isometric Art Viewer meant to replace the text representation of objects present in the game.
		\end{itemize}
	\item 11/12/16
		\begin{itemize}
			\item Version 1.7 Release
				\begin{itemize}
					\item Bug Fixes
				\end{itemize}
		\end{itemize}
\end{itemize}

\section{{\color{blue}Logistics}}

\subsection{{\color{blue}Resources}}

\begin{itemize}
	\item Collaboration
		\begin{itemize}
			\item \href{https://slack.com/}{Slack, Team Messenging App}
			\item \href{https://github.com/}{Github, Social Coding \& Issue Tracker}
		\end{itemize}
	\item Theory
		\begin{itemize}
			\item \href{http://baxter-academy.org/faculty#hlarsson}{Hal}
			\item Rob
			\item Rubber Duck
		\end{itemize}
	\item Learn to Code Resources
		\begin{itemize}
			\item \href{https://www.jetbrains.com/pycharm-edu/}{PyCharm Edu}
			\item \href{https://codehs.com/}{CodeHS}
			\item \href{http://www.codecademy.com/}{\framebox[1.1\width]{code}\underline{c}ademy}
		\end{itemize}
	\item Development Tools
		\begin{itemize}
			\item Linux
			\item \href{https://atom.io/}{atom}
			\item \href{https://www.jetbrains.com/pycharm/}{PyCharm}
			\item \href{http://www.syntevo.com/smartgit/}{SmartGit}
		\end{itemize}
\end{itemize}

\subsection{{\color{blue}Budget}}

This is the only budget the entire And/Ore Project has, as these are the only expenses.

\begin{center}
    \begin{tabular}{ | l | l | l | l | l |}
    \hline
    Vendor & Item & Cost & Quantity & Total Cost\\ \hline
    Digital Ocean & Sleipnir Node & \$10/month & 1 & \$10/month \\ \hline
    Digital Ocean & Panagoul Node & \$10/month & 1 & \$10/month \\ \hline
    Digital Ocean & Ulysses Node & \$10/month & 1 & \$10/month \\ \hline
    Digital Ocean & Reinforced Node & \$20/month & 1 & \$20/month \\ \hline
    Digital Ocean & Absolution Node & \$5/month & 1 & \$5/month \\ \hline
    Digital Ocean & Cynosural Node & \$5/month & 1 & \$5/month \\ \hline
    Digital Ocean & Erebus Node & \$5/month & 1 & \$5/month \\ \hline
    \space & \space & \space & \space & \space \\ \hline
    \space & \space & \space & \space & \$65/month \\ \hline
    \hline
    \end{tabular}
\end{center}

\end{document}