\documentclass[11pt]{article}
\title{\textbf{{\color{blue}Flex Friday Exploratory Project Proposal}}}
\author{And/Ore Playtesting Team}
\date{}
\usepackage{tikz}
\usepackage{gensymb}
\usepackage{physics}
\usepackage{color}
\usepackage{tabto}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\begin{document}

\maketitle

\section{{\color{blue}Vision}}

\subsection{{\color{blue}Purpose}}

The group as whole wants to learn more about what game development is like, help And/Ore become a “better” game, and get people interested in game development.  We hope to make the game more  successful by providing information about the way the game works to the front and back end teams.This will help to make the game fun for players by providing many different features and gameplay styles.


\subsection{{\color{blue}Goal}}

\begin{itemize}
\item Make the game more compelling, and less repetitive by informing the back end team of flaws and possible new features
\item Make game less confusing (via wiki/legend)
\item Increased number of items.
\item Make sure you cannot block off half the map and not be able to break whatever is blocking it.
\end{itemize}

\section{{\color{blue}Approach}}


\subsection{{\color{blue}Objectives}}

\begin{itemize}
	\item All players in playtest will feel like the game is balanced.
	\item Write the wiki with game mechanics listed clearly.
\end{itemize}

\subsection{{\color{blue}Team}}

{\large {\color{orange}Alec Wilson}}

Alec is good at finding things that are not fun.


{\large {\color{orange}Sam Nunn}}

Sam plays video games and is interested in game development.

{\large {\color{orange}Owen Crowley}}

Owen is very into game development and will work hard to learn and stay on task.

{\large {\color{orange}Quinn Balsam}}

Quinn can be helpful, but also has a tendency to procrastinate.

{\large {\color{orange}Alex Pape}}

Alex is here to learn about game development and experience it while he still can.

\subsection{{\color{blue}Milestones}}

\begin{itemize}
	\item 10/01/16
		\begin{itemize}
			\item Version 1.4 Release
				\begin{itemize}
					\item Introduced feeding treats to your neural network.
					\item Split up game server for better performance and to introduce the start of multiple playable worlds.
				\end{itemize}
		\end{itemize}
	\item 10/15/16
		\begin{itemize}
			\item Version 1.5 Release
				\begin{itemize}
					\item Bug Fixes
					\item The release of sphere, an admin panel for game moderators
					\item New feature to heal others/buildings.
				\end{itemize}
		\end{itemize}
	\item 10/29/16
		\begin{itemize}
			\item Version 1.6 Release
				\begin{itemize}
					\item Chat Introduced
					\item Bug Fixes
				\end{itemize}
		\end{itemize}
	\item 11/11/16
		\begin{itemize}
			\item Prototype of Isometric Art Viewer meant to replace the text representation of objects present in the game.
		\end{itemize}
	\item 11/12/16
		\begin{itemize}
			\item Version 1.7 Release
				\begin{itemize}
					\item Bug Fixes
				\end{itemize}
		\end{itemize}
\end{itemize}

\section{{\color{blue}Logistics}}

\subsection{{\color{blue}Resources}}

\begin{itemize}
	\item Theory
		\begin{itemize}
			\item \href{http://baxter-academy.org/faculty#hlarsson}{Hal}
			\item Rob
			\item Rubber Duck
		\end{itemize}
	\item Learn to Code Resources
		\begin{itemize}
			\item \href{https://www.jetbrains.com/pycharm-edu/}{PyCharm Edu}
			\item \href{https://codehs.com/}{CodeHS}
			\item \href{http://www.codecademy.com/}{\framebox[1.1\width]{code}\underline{c}ademy}
		\end{itemize}
	\item Development Tools
		\begin{itemize}
			\item Windows
			\item Linux
			\item \href{https://atom.io/}{atom}
			\item \href{https://www.jetbrains.com/pycharm/}{PyCharm}
			\item \href{http://www.syntevo.com/smartgit/}{SmartGit}
		\end{itemize}
\end{itemize}

\subsection{{\color{blue}Budget}}

The Backend team of And/Ore is the only team with expenses.

\end{document}