\documentclass[11pt]{article}
\title{\textbf{{\color{blue}Flex Friday Exploratory Project Proposal}}}
\author{And/Ore Playtesting Team}
\date{}
\usepackage{tikz}
\usepackage{gensymb}
\usepackage{physics}
\usepackage{color}
\usepackage{tabto}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\begin{document}

\maketitle

\section{{\color{blue}Vision}}

\subsection{{\color{blue}Purpose}}

The purpose of the QA Team is to find and report bugs in And/Ore to make the game more enjoyable, and less frustrating. They will explore the code of the game looking for mistakes that would cause bugs to happen. This will help us to learn more about code in general. If they have trouble, they can ask Hal for advice, and the team will use that information to make a fun and entertaining game.



\subsection{{\color{blue}Goal}}

\begin{itemize}
	\item Help create a bug-free game
		\begin{itemize}
			\item Will find and replicate bugs
			\item Will learn how to write proper bug reports
		\end{itemize}
	\item To get hands on experience on what it is liek to make and develop a game.
		\begin{itemize}
			\item Will become familiar with the codebase by asking/looking up ways to read the algorithm
			\item Will learn how to use collaboration tools productively.
			\item Will recommend solutions to the backend team
		\end{itemize}
\end{itemize}

\section{{\color{blue}Approach}}


\subsection{{\color{blue}Objectives}}

\begin{itemize}
	\item Each member of the team wants to have found ten bugs.
	\item The team wants to be able to understand the code of the game enough to explain to a non-coder.
	\item Each team member needs to understand git[hub] well enough to explain bugs properly.
\end{itemize}

\subsection{{\color{blue}Team}}

{\large {\color{orange}Xander}}

{\large {\color{red}MISSING}}

{\large {\color{orange}Owen Watson}}

Starting with a blank slate, Owen is interested in the project because he'd like to learn more about what it takes and the challenges faced when designing a video game.


{\large {\color{orange}Josh Erickson-Harris}}

While having no previous background experience, Josh is interested in the project due to his curiosity in game design.

{\large {\color{orange}Bodhi Wilkins}}

Coming from a novice coding background, Bodhi is interested in this project because of his interest in video games and curiosity in wanting to know how they're made.

{\large {\color{orange}Liam Connor-Schaefer}}

Liam has experience in finding bugs in games, and isn't a beginner to coding, so he's counting on building on top of his pre-existing knowledge.

\subsection{{\color{blue}Milestones}}

\begin{itemize}
	\item 10/01/16
		\begin{itemize}
			\item Version 1.4 Release
				\begin{itemize}
					\item Introduced feeding treats to your neural network.
					\item Split up game server for better performance and to introduce the start of multiple playable worlds.
				\end{itemize}
		\end{itemize}
	\item 10/15/16
		\begin{itemize}
			\item Version 1.5 Release
				\begin{itemize}
					\item Bug Fixes
					\item The release of sphere, an admin panel for game moderators
					\item New feature to heal others/buildings.
				\end{itemize}
		\end{itemize}
	\item 10/29/16
		\begin{itemize}
			\item Version 1.6 Release
				\begin{itemize}
					\item Chat Introduced
					\item Bug Fixes
				\end{itemize}
		\end{itemize}
	\item 11/11/16
		\begin{itemize}
			\item Prototype of Isometric Art Viewer meant to replace the text representation of objects present in the game.
		\end{itemize}
	\item 11/12/16
		\begin{itemize}
			\item Version 1.7 Release
				\begin{itemize}
					\item Bug Fixes
				\end{itemize}
		\end{itemize}
\end{itemize}

\section{{\color{blue}Logistics}}

\subsection{{\color{blue}Resources}}

\begin{itemize}
	\item Collaboration
		\begin{itemize}
			\item \href{https://slack.com/}{Slack, Team Messenging App}
			\item \href{https://github.com/}{Github, Social Coding \& Issue Tracker}
		\end{itemize}
	\item Theory
		\begin{itemize}
			\item \href{http://baxter-academy.org/faculty#hlarsson}{Hal}
			\item Rob
			\item Rubber Duck
		\end{itemize}
	\item Learn to Code Resources
		\begin{itemize}
			\item \href{https://www.jetbrains.com/pycharm-edu/}{PyCharm Edu}
			\item \href{https://codehs.com/}{CodeHS}
			\item \href{http://www.codecademy.com/}{\framebox[1.1\width]{code}\underline{c}ademy}
		\end{itemize}
	\item Development Tools
		\begin{itemize}
			\item Windows
			\item Linux
			\item \href{https://atom.io/}{atom}
			\item \href{https://www.jetbrains.com/pycharm/}{PyCharm}
			\item \href{http://www.syntevo.com/smartgit/}{SmartGit}
		\end{itemize}
\end{itemize}

\subsection{{\color{blue}Budget}}

The Backend team of And/Ore is the only team with expenses.

\end{document}